Trauma treatment delay

### 2023-11-23 manuscriptlongversion.Rmd
text

In this study, one of the limitations was the amount of people having
the recorded outcome being quite small, leading to having the variables
being split up into

>>>>

In this study, one of the limitations was the amount of people having
the recorded outcome being quite small, leading to having the variables
being split up into two groups for the logistical regression.
Furthermore, the original plan was to divide RR, SBP and GCS into
revised trauma score (RTS) categories, from 1-4. However, many of the
RTS variables had few to no patients with the observed outcome. This led
to separation in the logistical regression in these variables, referring
to when an outcome variable separates a predictor variable completely,
which occurs when the predictor is only associated with one outcome
value. In the case it was RTS 3 and 4, which left RTS 1 and 2 with
confidence intervalls of 0.00 to infinity.
